---
output:
  pdf_document: default
  html_document: default
---

# MIS 64018: Assignment_3
# Post-optimality and sensitivity analysis for LP problems

##by Eyob Tadele

##10/09/2021

### Solving the problem using lpsolve, or any other equivalent library in R.
Loading the lpSolveAPI library
```{r}
library(lpSolveAPI)
```
Reading the lp formulation from weigelt.lp file and assign it to w 
```{r}
p <- read.lp("weigelt.lp")
p
```
### Question 1: Solve the problem using lpsolve library in r.
```{r}
solve(p)    # if output is 0, it means there's a successful solution
# the objective value for this problem is:
get.objective(p)        
# the values of decision variables for the optimal solution are:
get.variables(p)        
```
### Question 2: Identify shadow prices, dual solution, and reduced costs.
```{r}
# the constraint RHS values are as follows: 
get.constraints(p)      
# the shadow prices are the following(the last 9 values are for the non-negativity constraints):
get.sensitivity.rhs(p) 
# the reduced costs are as follows: 
get.sensitivity.obj(p)  
```
### Question 3: Further, identify the sensitivity of the above prices and costs.
The range of reduced cost values that maintain the optimal solution are as follows:

Constraints   |   Range
-----------   |   ----------------
L1            |   [360,460] 
M1            |   [345,420] 
S1            |   [-infinity, 324]
L2            |   [-infinity, 460]
M2            |   [345,420]
S2            |   [252,324]
L3            |   [-infinity, 780]
M3            |   [-infinity, 480]
S3            |   [204, +infinity]



The range of shadow prices for constraints(C) 1 to 11, that maintain the optimal solution are as follows: 

Constraints   |   Range
-----------   |   ----------------
C1            |   [-infinity, +infinity]
C2            |   [-infinity, +infinity]
C3            |   [-infinity, +infinity]
C4            |   [11222.22, 13888.9]
C5            |   [11500, 12500]
C6            |   [4800, 5181.8]
C7            |   [-infinity, +infinity]
C8            |   [-infinity, +infinity]
C9            |   [-infinity, +infinity]
C10           |   [-25000, 25000]
C11           |   [-12500, 12500]

### Question 4: Formulate the dual of the above problem and solve it. Does it agree with what you observed for the primal problem?

Reading the lp formulation from weigelt_d.lp file and assign it to w 
```{r}
d <- read.lp("weigelt_d.lp")
d
```
Solving the dual problem
```{r}
solve(p)    # if output is 0, it means there's a successful solution

# the objective value for this problem is:
get.objective(p)        

# the values of decision variables for the optimal solution are:
get.variables(p)        
```

### The values I observed from solving the dual does not fall in line with the results of the primal problem. The optimal value of the primal is 696000 and the dual is 698000. 
### Also, the shadow prices of the primal and the decision variables of the dual are not the same either.