---
title: 'MIS 64018: Assignment_4: Transportation / Transshipment problem '
author: "Eyob Tadele"
date: "10/22/2021"
output:
  pdf_document: default
  html_document: default
---

### Project Objective
The purpose of this assignment is to formulate and solve a transportation / transshipment problem.

#### Problem Formulation:
Since we are required to find a solution that minimizes the combined cost of production and shipment, this is obviously a minimization problem. In addition, we can see that Plants A and B have a combined production capacity(i.e. supply) of 220. Whereas, the warehouses have a combined demand of 210. This makes for an unbalanced problem which requires introducing a dummy warehouse. The formulation below puts that into consideration.
&nbsp;

Plant         | W1 | W2 | W3 | W4* | Output 
------------- | ---| ---| ---| ----| ------
Plant A       | 22 | 14 | 30 | M(0)| 100 
Plant B       | 16 | 20 | 24 | M(0)| 120 
------------- | ---| ---| ---| ----| ------
Demand        | 80 | 60 | 70 | 10  | 

Objective function: \
Min: Z = 622 x11 + 614 x12 + 630 x13 + 641 x21 + 645 x22 + 649 x23
Subject to: \
x11 + x12 + x13 + M14 = 100 \
x21 + x22 + x23 + M24 = 120 \
x11 + x21 = 80 \
x12 + x22 = 60 \
x13 + x23 = 70 \
M14 + M24 = 10 \
(x11,x12,x13,x21,x22,x23) >= 0 \

### Solving the problem using lpsolve, or any other equivalent library in R.
Loading the lpSolveAPI library
```{r}
library(lpSolveAPI)
```

```
/*Objective function*/
Min: 622 x11 + 614 x12 + 630 x13 + 641 x21 + 645 x22 + 649 x23;
/*Constraints*/
x11 + x12 + x13 + M14 = 100;
x21 + x22 + x23 + M24 = 120;
x11 + x21 = 80;
x12 + x22 = 60;
x13 + x23 = 70;
M14 + M24 = 10;
```

Reading the lp formulation from HS.lp file and assign it to p
```{r}
p <- read.lp("HS.lp")
p
```
### Question 1: Solve this transportation problem using lpsolve library in r.
```{r}
solve(p)
# the objective value for this problem is:
get.objective(p)        
# the values of decision variables for the optimal solution are:
get.variables(p)
```

#### The overall total cost is $132,790. As for shipments from plants to warehouses, Plant A should ship 60 AEDs to Warehouse2 and 40 AEDs to Warehouse3; Plant B should ship 80 AEDs to Warehouse1 and 30 to Warehouse3.
#### The last two values for the decision variables are shipments for the dummy Warehouse4.

\newpage

## Part 2: Oil Distribution transshipment problem.

```
/*Objective Function*/
Min: 1.52 X1 + 1.60 X2 + 1.40 X3 + 1.7 X4 + 1.63 X5 + 1.55 X6 + 1.45 X7 + 1.57 X8 + 1.30 X9 + 
  5.15 X10 + 5.69 X11 + 6.13 X12 + 5.63 X13 + 5.80 X14 + 5.12 X15 + 5.47 X16 + 6.05 X17 + 6.12 X18 + 
  5.71 X19 + 5.32 X20 + 6.16 X21 + 6.25 X22 + 6.17 X23 + 5.87 X24;
/*Constraints*/
X1 + X2 + X3 = 93;
X4 + X5 + X6 = 88;
X7 + X8 + X9 = 95;
X10 + X15 + X20 = 30;
X11 + X16 + X21 = 57;
X12 + X17 + X22 = 48;
X13 + X18 + X23 = 91;
X14 + X19 + X24 = 48;
M16 + M26 + M36 = 2;
X1 + X4 + X7 - X10 - X11 - X12 - X13 - X14 - M16 = 0;
X2 + X5 + X8 - X15 - X16 - X17 - X18 - X19 - M26 = 0;
X3 + X6 + X9 - X20 - X21 - X22 - X23 - X24 - M36 = 0;
```

Reading the lp formulation from TOD.lp file and assign it to x
```{r}
x <- read.lp("TOD2.lp")
x
```
### Question 1: Solve this transportation problem using lpsolve library in r.
```{r}
solve(x)
# the objective value for this problem is:
get.objective(x)        
# the values of decision variables for the optimal solution are:
get.variables(x)
```
#### The minimum cost is 1966.68. Wells 1 and 2 are operating at capacity. Note that the last three values for the decision variables are for the dummy refineries. 