---
title: 'MIS 64018: Assignment_2: Solving LP problems'
author: "Eyob Tadele"
date: "10/003/2021"
output:
  pdf_document: default
  html_document: default
---

## Question 3:

### a. Define the decision variables:

The decision variables are what products (L, M, S) to be produced, at which plant (P1, P2, P3). 
		LP1: Large at Plant1
		LP2: Large at Plant2
		LP3: Large at Plant3
		MP1: Medium at Plant1
		MP2: Medium at Plant2
		MP3: Medium at Plant3
		SP1: Small at Plant1
		SP2: Small at Plant2
		SP3: Small at Plant3

### b. The objective funtion for this problem is to maximize profit by producing optimum amounts of each product in the respective plants.

	MAX z: 

	420xLP1 + 420xLP2 + 420xLP3 + 360xMP1 + 360xMP2 + 360xMP3 + 300xSP1 + 300xSP2 + 300xSP3 

	S.T.

	**capacity to produce constraint:** 
	LP1 + MP1 + SP1 <= 750
	LP2 + MP2 + SP2 <= 900
	LP3 + MP3 + SP3 <= 450

	**available storage constraint:**
	20 x LP1 + 15 x MP1 + 12 x SP1 <= 750
	20 x LP2 + 15 x MP2 + 12 x SP2 <= 900
	20 x LP3 + 15 x MP3 + 12 x SP3 <= 450

	**sales constraint:**
	LP1 + LP2 + LP3	<= 900
	MP1 + MP2 + MP3 <= 1200
	SP1 + SP2 + SP3 <= 750

	Percentage of excess capacity constraint: 
	i.e. (Products/Plant)x100% should be the same across all plants

	100 x ((LP1 + MP1 + SP1)/750) = ((LP2 + MP2 + SP2)/900) x 100
	re-arranging the equation:

		(LP1 + MP1 + SP1)/750 = (LP2 + MP2 + SP2)/900

		(1/750) x (LP1 + MP1 + SP1) = (1/900) x (LP2 + MP2 + SP2)

		0.0013 x LP1 + 0.0013 x MP1 + 0.0013 xSP1 - 0.0011 x LP1 - 0.0011 x MP1 - 0.0011 x SP1 = 0

		doing the same as above between (P1,P3) and (P2,P3):
  
  **Percentage of excess capacity constraint:**
	0.0013 x LP1 + 0.0013 x MP1 + 0.0013 xSP1 - 0.0022 x LP1 - 0.0022 x MP1 - 0.0022 x SP1 = 0
  0.0011 x LP1 + 0.0011 x MP1 + 0.0011 xSP1 - 0.0022 x LP1 - 0.0022 x MP1 - 0.0022 x SP1 = 0
	0.0013 x LP1 + 0.0013 x MP1 + 0.0013 xSP1 - 0.0011 x LP1 - 0.0011 x MP1 - 0.0011 x SP1 = 0
	
### Solving the problem using lpsolve, or any other equivalent library in R.

Loading the lpSolveAPI library
```{r}
library(lpSolveAPI)
```
Reading the lp formulation from assignment2.lp file and assign it to WeigeltProd 
```{r}
WeigeltProd <- read.lp("assignment2.lp")
WeigeltProd
```
Solve the lp model
```{r}
solve(WeigeltProd)    # if output is 0, it means there's a successful solution
get.objective(WeigeltProd)        # get objectiv
get.variables(WeigeltProd)        # get values of decision variables
get.constraints(WeigeltProd)      # get constraint RHS values
```
	